---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kgsr
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Linux Build Status](https://travis-ci.org/emraher/kgsr.svg?branch=master)](https://travis-ci.org/emraher/kgsr)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/4ejevtp69fcrr31o?svg=true)](https://ci.appveyor.com/project/emraher/kgsr)
[![](http://www.r-pkg.org/badges/version/kgsr)](http://www.r-pkg.org/pkg/kgsr)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/kgsr)](http://www.r-pkg.org/pkg/kgsr)
[![Coverage status](https://coveralls.io/repos/github/emraher/kgsr/badge.svg)](https://coveralls.io/r/emraher/kgsr?branch=master)

## Disclaimer

This software is in no way affiliated, endorsed, or approved by the [Kansas Geological Survey - The University of Kansas](http://www.kgs.ku.edu/). It comes with absolutely no warranty.


## Overview

`kgsr` is an R "interface" to KGS. It can download data from [Kansas Geological Survey - The University of Kansas](http://www.kgs.ku.edu/).



## Installation

You can install `kgsr` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("emraher/kgsr")
```

## Data on KGS

* [Water](http://www.kgs.ku.edu/Hydro/hydroIndex.html)
    * [Kansas Master Ground-Water Well Inventory](http://hercules.kgs.ku.edu/geohydro/master_well/index.cfm)
* [Energy](http://www.kgs.ku.edu/PRS/petroIndex.html)
    * [State Production and Historical Info](http://www.kgs.ku.edu/PRS/petro/state.html)
    * [County Production](http://www.kgs.ku.edu/PRS/petro/interactive.html)
    * [Production from Kansas Oil and Gas Fields](http://www.kgs.ku.edu/Magellan/Field/index.html)
    * [Gas Storage Fields in Kansas](http://chasm.kgs.ku.edu/ords/oil.ogf4.GasStorage)
    * [Production from Kansas Oil and Gas Leases](http://www.kgs.ku.edu/Magellan/Field/lease.html)
    * [Kansas Oil and Gas Production by Operator](http://www.kgs.ku.edu/Magellan/Field/operators.html)
    * [Master List of Oil and Gas Wells in Kansas](http://www.kgs.ku.edu/Magellan/Qualified/index.html)
* [Geology](http://www.kgs.ku.edu/General/geologyIndex.html)
* [Geophysics](http://www.kgs.ku.edu/Geophysics/esIndex.html)

## Usage 

### Download data from [Kansas Master Ground-Water Well Inventory](http://hercules.kgs.ku.edu/geohydro/master_well/index.cfm)

There are two functions in the package which retrieve data from Kansas Master Ground-Water Well Inventory.

```{r water, eval = TRUE, warning=TRUE, error=TRUE, message=TRUE, cache=TRUE}
library(kgsr)
dt <- mwi("allen")
dt

# -----------------------------------------------------------------------------
# Ignoring unmatched file
# -----------------------------------------------------------------------------
dt <- mwi("Cowley")
dt

# -----------------------------------------------------------------------------
# Wrong county name
# -----------------------------------------------------------------------------
dt <- mwi("alen")

# -----------------------------------------------------------------------------
# Download with given township, range, range direction, and section (optional).
# -----------------------------------------------------------------------------
dt <- mwi_plss(township = "1", range = "1", range_dir = "W", section = "1", unmatched = TRUE)
dt
```

### Download data from [Master List of Oil and Gas Wells in Kansas](http://www.kgs.ku.edu/Magellan/Qualified/index.html)
```{r energy, eval = TRUE, warning=TRUE, error=TRUE, message=TRUE, cache=TRUE}
library(kgsr)
dt <- ogw(township = "1", range = "1")
dt

dt <- ogw(county = "allen", welltype = "OIL")
dt
```

## Code of Conduct
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
