---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kgsr

[![Build Status](https://travis-ci.org/emraher/kgsr.svg?branch=master)](https://travis-ci.org/emraher/kgsr)
[![Coverage status](https://codecov.io/gh/emraher/kgsr/branch/master/graph/badge.svg)](https://codecov.io/github/emraher/kgsr?branch=master)
[![Coverage status](https://coveralls.io/repos/github/emraher/kgsr/badge.svg)](https://coveralls.io/r/emraher/kgsr?branch=master)
[![AppVeyor Build Status](https://ci.appveyor.com/emraher/kgsr)](https://ci.appveyor.com/api/projects/status/github//emraher/kgsr/?branch=master&svg=true)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Disclaimer

This software is in no way affiliated, endorsed, or approved by the [Kansas Geological Survey - The University of Kansas](http://www.kgs.ku.edu/). It comes with absolutely no warranty.

## Overview

`kgsr` is an R "interface" to KGS. It can download data from [Kansas Master Ground-Water Well Inventory](http://hercules.kgs.ku.edu/geohydro/master_well/index.cfm).

## Installation

You can install `kgsr` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("emraher/kgsr")
```
## Usage 

There is only one function in the package which retrieves data from KGS Kansas Master Ground-Water Well Inventory.

```{r usage, eval = TRUE, warning=TRUE, error=TRUE, message=TRUE}
library(kgsr)
dt <- mwi("allen")
dt

# -----------------------------------------------------------------------------
# Ignoring unmatched file
# -----------------------------------------------------------------------------
dt <- mwi("Cowley")
dt

# -----------------------------------------------------------------------------
# Wrong county name
# -----------------------------------------------------------------------------
dt <- mwi("alen")
```
## Code of Conduct
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
